\begin{rSection}{Presentations}

\textbf{Talks:}

\textbf{LeMaitre, Philip A.}. “A Universal Quantum Computer From Relativistic Motion”. \\
15th Relativistic Quantum Information North Conference, University of Naples Federico II, Napoli, Italy \hfill\textit{{June. 2025}}

\textbf{LeMaitre, Philip A.}. “Physical Characteristics and Manifestations of Agents”. \\
Innsbruck-Konstanz-Hannover Meeting on Physics and Philosophy, Maria Waldrast, Austria \hfill\textit{{Sep. 2024}}

\textbf{LeMaitre, Philip A.}. “A Universal Quantum Computer From Relativistic Motion”. \\
14th Relativistic Quantum Information North Conference, Charles University, Prague, Czechia \hfill\textit{{Aug. 2024}}

\textbf{LeMaitre, Philip A.}. “A Multi-Excitation Projective Simulation Agent”. \\
DPG Spring Meeting 2024, T\"U Berlin, Berlin, Germany \hfill\textit{{Mar. 2024}}

\textbf{LeMaitre, Philip A.}. “Spontaneous Spherical Symmetry-Breaking in Open-Shell Atoms Through Polymer Self-Consistent Field Theory”. \\
36th Symposium on Chemical Physics, University of Waterloo, Waterloo, Canada \hfill\textit{{Nov. 2022}}

\textbf{LeMaitre, Philip A.}. “Atomic Shell Structure in a Polymer-Based Approach to Orbital-Free Density-Functional Theory”. \\
2022 Canadian Association of Physicists Congress, McMaster University, Hamilton, Canada \hfill\textit{{June 2022}}

\textbf{LeMaitre, Philip A.}. “Thin-Shells as Neutron Stars: A Simple Stellar Model With Great Insight”. \\
Canadian Undergraduate Physics Conference 2019, McGill University, Montreal, Canada \hfill\textit{{Nov. 2019}}

\textbf{Posters:}

\textbf{LeMaitre, Philip A.}. “A Universal Quantum Computer from Relativistic Motion”. \\
QISS 2025 Conference, University of Vienna, Vienna, Austria \hfill\textit{{April 2025}}

\textbf{LeMaitre, Philip A.}. “Quantum Multi-Excitation Projective Simulation”. \\
6th Seefeld Quantum Information Workshop, Wellnesshotel Schönruh, Seefeld, Austria \hfill\textit{{June 2024}}

\textbf{LeMaitre, Philip A.}. “Towards a Multi-Excitation Projective Simulation Agent”. \\
Innsbruck-Konstanz Meeting on Physics and Philosophy, Lamm Hotel, Bregenz, Austria \hfill\textit{{Sep. 2023}}

\end{rSection}